---
title: "Hotel Revenue Management"
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: scroll
    css: styles.css
    theme:
      version: 5
      bootswatch: "lux"
---

```{r setup, include=FALSE}
library(flexdashboard)
library(shinydashboard)
library(shiny)
library(echarts4r)
library(highcharter)
library(reactable)
library(reactablefmtr)
library(fontawesome)
```

```{r}
source("C:/Users/AYOMIDE/Documents/R/R_Projects/hotel_revenue/hotel_dashboard/functions.R",
       local = knitr::knit_global())

source("C:/Users/AYOMIDE/Documents/R/R_Projects/hotel_revenue/hotel_dashboard/function_ui.R",
       local = knitr::knit_global())

source("C:/Users/AYOMIDE/Documents/R/R_Projects/hotel_revenue/hotel_dashboard/global.R",
       local = knitr::knit_global())
```


```{r}
hr <- purrr::map_dfr(
  c(1, 2, 3),
  ~readxl::read_excel("~/DataG/hotel_222/Hotel Revenue Management.xlsx", sheet = .x)
)

discount <- readxl::read_excel("~/DataG/hotel_222/Hotel Revenue Management.xlsx", 
                               sheet = 4, skip = 1)

meal_cost <- readxl::read_excel("~/DataG/hotel_222/Hotel Revenue Management.xlsx", 
                                sheet = 5, skip = 1)

full_country_name <- readr::read_csv("C:/Users/AYOMIDE/Documents/DataG/country_code.csv")

discount <- discount |>
  dplyr::mutate(Discount = as.numeric(Discount)) |>
  dplyr::rename(discount_applied = Discount)

meal_cost <- meal_cost |>
  dplyr::mutate(Cost = as.numeric(Cost)) |>
  dplyr::rename(meal_cost = Cost)

month_number <- setNames(month.name, 1:12)

names_country <- dplyr::select(hr, country) |>
  dplyr::left_join(full_country_name, by = c("country" = "ISO3"), keep = TRUE) |>
  dplyr::select(country, country_name) |>
  tibble::deframe()

hr <- hr |>
  dplyr::inner_join(discount, by = "market_segment") |>
  dplyr::inner_join(meal_cost, by = "meal") |>
  dplyr::mutate(temp_month = as.character(forcats::fct_recode(arrival_date_month, !!!month_number)),
                
                arrival_date = stringr::str_glue("{arrival_date_year}-{temp_month}-{arrival_date_day_of_month}"),
                
                arrival_date = lubridate::as_date(arrival_date),
                
                avg_daily_rate = dplyr::case_when(is.na(adr) ~ `AVG Daily Rate`,
                                                  !is.na(adr) ~ adr,
                                                  TRUE ~ 1000000),
                
                children = dplyr::case_when(is.na(children) ~ 0, TRUE ~ children),
                
                stay_nights = stays_in_week_nights + stays_in_weekend_nights,
                
                revenue = (avg_daily_rate * stay_nights) + meal_cost,
                
                discount = revenue * discount_applied,
                
                net_revenue = revenue - discount,
                
                country = dplyr::if_else(country == "NULL", "Undefined", country),
                nationality = names_country,
                nationality = dplyr::case_when(country == "CN" ~ "China",
                                               country == "GGY" ~ "Guernsey",
                                               country == "IMN" ~ "isle of Man",
                                               country == "MYT" ~ "Mayotte",
                                               country == "Undefined" ~ "Undefined",
                                               TRUE ~ nationality)
  ) |>
  dplyr::select(-c(temp_month, adr, `AVG Daily Rate`, country))
```


# All {data-navmenu="Overview" data-orientation="columns"}


## overview_all_column1 {data-height=400 data-width=400}

### Revenue
```{r}
revenue_box(
  rev_variable_summary(hr, "net_revenue"),
  rev_variable_summary(hr, "net_revenue", percent = TRUE),
  rev_variable_summary(hr, "net_revenue", a_fun = "mean"),
  
  rev_variable_summary(hr, "avg_daily_rate"),
  rev_variable_summary(hr, "avg_daily_rate", a_fun = "min"),
  rev_variable_summary(hr, "avg_daily_rate", a_fun = "mean"),
  
  rev_variable_summary(hr, "discount"),
  rev_variable_summary(hr, "discount", a_fun = "mean"),
  rev_variable_summary(hr, "discount", a_fun = "max"),
  
  rev_variable_summary(hr, "meal_cost"),
  rev_variable_summary(hr, "meal_cost", percent = TRUE),
  rev_variable_summary(hr, "meal_cost", a_fun = "max")
)

```

### Reservations
```{r}
stays <- days_stay_description(hr)

reservation_box(
  res_status_description(hr, "Check-Out"),
  res_status_description(hr, "Canceled"),
  res_status_description(hr, "No-Show"),
  
  lead_time_description(hr, "lead_time", a_fun = "mean"),
  lead_time_description(hr, "lead_time", a_fun = "max"),
  lead_time_description(hr, "waiting_list", a_fun = "max"),
  
  booking_changes_description(hr, "changed"),
  booking_changes_description(hr, "no_changes"),
  booking_changes_description(hr, "precent"),
  
  stays$median,
  stays$minimum,
  stays$maximum
)

```

### Guest
```{r}
guest_box(
  guest_description(hr, "all"),
  guest_description(hr, "adult"),
  guest_description(hr, "children"),
  
  repeated_guest_description(hr, "repeated"),
  repeated_guest_description(hr, "no_repeat"),
  repeated_guest_description(hr, "percent_repeat"),
  
  nationality_description(hr, "country"),
  nationality_description(hr, "continent"),
  nationality_description(hr, "top_national"),
  
  special_request_description(hr, "total"),
  special_request_description(hr, "max"),
  special_request_description(hr, "precent")
)
```


## overview_all_column2 {data-height=400 data-width=600}

###  {.no-title}
```{r}
tabset_panel_output(
  arrival_date_revenue(hr, "net_revenue", 2020, colr = c(rev_colr1, rev_colr2)),
  
  arrival_date_revenue(hr, "net_revenue", 2019, colr = c(rev_colr1, rev_colr2)),
  
  arrival_date_revenue(hr, "net_revenue", 2018, colr = c(rev_colr1, rev_colr2))
)
```

###  {.no-title}
```{r}
tabset_panel_output(
  arrival_count(hr, 2020, colr = c(res_colr1, res_colr2)),
  
  arrival_count(hr, 2019, colr = c(res_colr1, res_colr2)),
  
  arrival_count(hr, 2018, colr = c(res_colr1, res_colr2))
)
```

###  {.no-title}
```{r}
tabset_panel_output(
  n_guest_arrival_date(hr, 2020, a_fun = "sum", colr = c(gst_colr1, gst_colr2)),
  
  n_guest_arrival_date(hr, 2019, a_fun = "sum", colr = c(gst_colr1, gst_colr2)),
  
  n_guest_arrival_date(hr, 2018, a_fun = "sum", colr = c(gst_colr1, gst_colr2))
)
```



# City Hotel {data-navmenu="Overview" data-orientation="columns"}


## overview_ch_column1 {data-height=400 data-width=400}

### Revenue
```{r}
revenue_box(
  rev_variable_summary(hr, "net_revenue", "City Hotel"),
  rev_variable_summary(hr, "net_revenue", "City Hotel", percent = TRUE),
  rev_variable_summary(hr, "net_revenue", "City Hotel",  a_fun = "mean"),
  
  rev_variable_summary(hr, "avg_daily_rate", "City Hotel"),
  rev_variable_summary(hr, "avg_daily_rate", "City Hotel", a_fun = "min"),
  rev_variable_summary(hr, "avg_daily_rate", "City Hotel", a_fun = "mean"),
  
  rev_variable_summary(hr, "discount", "City Hotel"),
  rev_variable_summary(hr, "discount", "City Hotel", a_fun = "mean"),
  rev_variable_summary(hr, "discount", "City Hotel", a_fun = "max"),
  
  rev_variable_summary(hr, "meal_cost", "City Hotel"),
  rev_variable_summary(hr, "meal_cost", "City Hotel", percent = TRUE),
  rev_variable_summary(hr, "meal_cost", "City Hotel",  a_fun = "max")
)
```

### Reservations
```{r}
ch_stays <- days_stay_description(hr, "City Hotel")

reservation_box(
  res_status_description(hr, "Check-Out", "City Hotel"),
  res_status_description(hr, "Canceled", "City Hotel"),
  res_status_description(hr, "No-Show", "City Hotel"),
  
  lead_time_description(hr, "lead_time", "City Hotel", a_fun = "mean"),
  lead_time_description(hr, "lead_time", "City Hotel", a_fun = "max"),
  lead_time_description(hr, "waiting_list", "City Hotel", a_fun = "max"),
  
  booking_changes_description(hr, "changed", "City Hotel"),
  booking_changes_description(hr, "no_changes", "City Hotel"),
  booking_changes_description(hr, "precent", "City Hotel"),
  
  ch_stays$median,
  ch_stays$minimum,
  ch_stays$maximum
)
```

### Guest
```{r}
guest_box(
  guest_description(hr, "all", "City Hotel"),
  guest_description(hr, "adult", "City Hotel"),
  guest_description(hr, "children", "City Hotel"),
  
  repeated_guest_description(hr, "repeated", "City Hotel"),
  repeated_guest_description(hr, "no_repeat", "City Hotel"),
  repeated_guest_description(hr, "percent_repeat", "City Hotel"),
  
  nationality_description(hr, "country", "City Hotel"),
  nationality_description(hr, "continent", "City Hotel"),
  nationality_description(hr, "top_national", "City Hotel"),
  
  special_request_description(hr, "total", "City Hotel"),
  special_request_description(hr, "max", "City Hotel"),
  special_request_description(hr, "precent", "City Hotel")
)
```


## overview_ch_column2 {data-height=400 data-width=600}

###  {.no-title}
```{r}
tabset_panel_output(
  arrival_date_revenue(hr, "net_revenue", 2020, "City Hotel",
                       colr = c(rev_colr1, rev_colr2)),
  
  arrival_date_revenue(hr, "net_revenue", 2019, "City Hotel",
                       colr = c(rev_colr1, rev_colr2)),
  
  arrival_date_revenue(hr, "net_revenue", 2018, "City Hotel",
                       colr = c(rev_colr1, rev_colr2))
)
```

###  {.no-title}
```{r}
tabset_panel_output(
  arrival_count(hr, 2020, "City Hotel", colr = c(res_colr1, res_colr2)),
  
  arrival_count(hr, 2019, "City Hotel", colr = c(res_colr1, res_colr2)),
  
  arrival_count(hr, 2018, "City Hotel", colr = c(res_colr1, res_colr2))
)
```

###  {.no-title}
```{r}
tabset_panel_output(
  n_guest_arrival_date(hr, 2020, "City Hotel", a_fun = "sum",
                       colr = c(gst_colr1, gst_colr2)),
  
  n_guest_arrival_date(hr, 2019, "City Hotel", a_fun = "sum",
                       colr = c(gst_colr1, gst_colr2)),
  
  n_guest_arrival_date(hr, 2018, "City Hotel", a_fun = "sum",
                       colr = c(gst_colr1, gst_colr2))
)
```



# Resort Hotel {data-navmenu="Overview" data-orientation="columns"}


## overview_rh_column1 {data-height=400 data-width=400}

### Revenue
```{r}
revenue_box(
  rev_variable_summary(hr, "net_revenue", "Resort Hotel"),
  rev_variable_summary(hr, "net_revenue", "Resort Hotel", percent = TRUE),
  rev_variable_summary(hr, "net_revenue", "Resort Hotel",  a_fun = "mean"),
  
  rev_variable_summary(hr, "avg_daily_rate", "Resort Hotel"),
  rev_variable_summary(hr, "avg_daily_rate", "Resort Hotel", a_fun = "min"),
  rev_variable_summary(hr, "avg_daily_rate", "Resort Hotel", a_fun = "mean"),
  
  rev_variable_summary(hr, "discount", "Resort Hotel"),
  rev_variable_summary(hr, "discount", "Resort Hotel", a_fun = "mean"),
  rev_variable_summary(hr, "discount", "Resort Hotel", a_fun = "max"),
  
  rev_variable_summary(hr, "meal_cost", "Resort Hotel"),
  rev_variable_summary(hr, "meal_cost", "Resort Hotel", percent = TRUE),
  rev_variable_summary(hr, "meal_cost", "Resort Hotel",  a_fun = "max")
)
```

### Reservations
```{r}
rh_stays <- days_stay_description(hr, "Resort Hotel")

reservation_box(
  res_status_description(hr, "Check-Out", "Resort Hotel"),
  res_status_description(hr, "Canceled", "Resort Hotel"),
  res_status_description(hr, "No-Show", "Resort Hotel"),
  
  lead_time_description(hr, "lead_time", "Resort Hotel", a_fun = "mean"),
  lead_time_description(hr, "lead_time", "Resort Hotel", a_fun = "max"),
  lead_time_description(hr, "waiting_list", "Resort Hotel", a_fun = "max"),
  
  booking_changes_description(hr, "changed", "Resort Hotel"),
  booking_changes_description(hr, "no_changes", "Resort Hotel"),
  booking_changes_description(hr, "precent", "Resort Hotel"),
  
  rh_stays$median,
  rh_stays$minimum,
  rh_stays$maximum
)
```

### Guest
```{r}
guest_box(
  guest_description(hr, "all", "Resort Hotel"),
  guest_description(hr, "adult", "Resort Hotel"),
  guest_description(hr, "children", "Resort Hotel"),
  
  repeated_guest_description(hr, "repeated", "Resort Hotel"),
  repeated_guest_description(hr, "no_repeat", "Resort Hotel"),
  repeated_guest_description(hr, "percent_repeat", "Resort Hotel"),
  
  nationality_description(hr, "country", "Resort Hotel"),
  nationality_description(hr, "continent", "Resort Hotel"),
  nationality_description(hr, "top_national", "Resort Hotel"),
  
  special_request_description(hr, "total", "Resort Hotel"),
  special_request_description(hr, "max", "Resort Hotel"),
  special_request_description(hr, "precent", "Resort Hotel")
)
```


## overview_rh_column2 {data-height=400 data-width=600}

###  {.no-title}
```{r}
tabset_panel_output(
  arrival_date_revenue(hr, "net_revenue", 2020, "Resort Hotel",
                       colr = c(rev_colr1, rev_colr2)),
  
  arrival_date_revenue(hr, "net_revenue", 2019, "Resort Hotel",
                       colr = c(rev_colr1, rev_colr2)),
  
  arrival_date_revenue(hr, "net_revenue", 2018, "Resort Hotel",
                       colr = c(rev_colr1, rev_colr2))
)
```

###  {.no-title}
```{r}
tabset_panel_output(
  arrival_count(hr, 2020, "Resort Hotel", colr = c(res_colr1, res_colr2)),
  
  arrival_count(hr, 2019, "Resort Hotel", colr = c(res_colr1, res_colr2)),
  
  arrival_count(hr, 2018, "Resort Hotel", colr = c(res_colr1, res_colr2))
)
```

###  {.no-title}
```{r}
tabset_panel_output(
  n_guest_arrival_date(hr, 2020, "Resort Hotel", a_fun = "sum",
                       colr = c(gst_colr1, gst_colr2)),
  
  n_guest_arrival_date(hr, 2019, "Resort Hotel", a_fun = "sum",
                       colr = c(gst_colr1, gst_colr2)),
  
  n_guest_arrival_date(hr, 2018, "Resort Hotel", a_fun = "sum",
                       colr = c(gst_colr1, gst_colr2))
)
```





# All {data-navmenu="Revenue" data-orientation="rows"}


## all_revenue_row1 {.tabset data-height=400}

### 2020
```{r}
arrival_date_revenue(hr, "avg_daily_rate", 2020,
                     colr = c(rev_colr$colr1, rev_colr$colr2))
```

### 2019
```{r}
arrival_date_revenue(hr, "avg_daily_rate", 2019,
                     colr = c(rev_colr$colr1, rev_colr$colr2))
```

### 2018 \| Average Daily Rate
```{r}
arrival_date_revenue(hr, "avg_daily_rate", 2018,
                     colr = c(rev_colr$colr1, rev_colr$colr2))
```


## all_revenue_row2 {.tabset data-height=400}

### 2020
```{r}
arrival_date_revenue(hr, "revenue", 2020,
                     colr = c(rev_colr$colr1, rev_colr$colr3))
```

### 2019
```{r}
arrival_date_revenue(hr, "revenue", 2019,
                     colr = c(rev_colr$colr1, rev_colr$colr3))
```

### 2018 \| Revenue
```{r}
arrival_date_revenue(hr, "revenue", 2018,
                     colr = c(rev_colr$colr1, rev_colr$colr3))
```


## all_revenue_row3 {.tabset data-height=400}

### 2020
```{r}
arrival_date_revenue(hr, "meal_cost", 2020,
                     colr = c(rev_colr$colr1, rev_colr$colr4))
```

### 2019
```{r}
arrival_date_revenue(hr, "meal_cost", 2019,
                     colr = c(rev_colr$colr1, rev_colr$colr4))
```

### 2018 \| Meal Cost
```{r}
arrival_date_revenue(hr, "meal_cost", 2018,
                     colr = c(rev_colr$colr1, rev_colr$colr4))
```


## all_revenue_row4 {.tabset data-height=400}

### 2020
```{r}
arrival_date_revenue(hr, "discount", 2020,
                     colr = c(rev_colr$colr1, rev_colr$colr5))
```

### 2019
```{r}
arrival_date_revenue(hr, "discount", 2019,
                     colr = c(rev_colr$colr1, rev_colr$colr5))
```

### 2018 \| Discount
```{r}
arrival_date_revenue(hr, "discount", 2018,
                     colr = c(rev_colr$colr1, rev_colr$colr5))
```



# City Hotel {data-navmenu="Revenue" data-orientation="columns"}


## rev_ch_column1 {data-height=375 data-width=500}

### Net Revenue
```{r}
net_revenue_dtms(hr, "market_segment", f_hotel = "City Hotel")
```

### Average Daily Rate
```{r}
avg_daily_rate_cmg(hr, "market_segment", f_hotel = "City Hotel")
```

### Meal Cost
```{r}
meal_revenue(hr, "customer_type", f_hotel = "City Hotel")
```

### Discount
```{r}
discount_ad(hr, "distribution_channel", f_hotel = "City Hotel")
```


## rev_ch_column2 {data-height="375" data-width="500"}

### .
```{r}
net_revenue_dtms(hr, "deposit_type", f_hotel = "City Hotel")
```

### .
```{r}
avg_daily_rate_cmg(hr, "customer_type", f_hotel = "City Hotel")
```

### .
```{r}
meal_revenue(hr, "meal", f_hotel = "City Hotel")
```

### .
```{r}
discount_ad(hr, "agent", f_hotel = "City Hotel")
```



# Resort Hotel {data-navmenu="Revenue" data-orientation="columns"}


## rev_ch_column1 {data-height=375 data-width=500}

### Net Revenue
```{r}
net_revenue_dtms(hr, "market_segment", f_hotel = "Resort Hotel")
```

### Average Daily Rate
```{r}
avg_daily_rate_cmg(hr, "market_segment", f_hotel = "Resort Hotel")
```

### Meal Cost
```{r}
meal_revenue(hr, "customer_type", f_hotel = "Resort Hotel")
```

### Discount
```{r}
discount_ad(hr, "distribution_channel", f_hotel = "Resort Hotel")
```


## rev_ch_column2 {data-height=375 data-width=500}

### .
```{r}
net_revenue_dtms(hr, "deposit_type", f_hotel = "Resort Hotel")
```

### .
```{r}
avg_daily_rate_cmg(hr, "customer_type", f_hotel = "Resort Hotel")
```

### .
```{r}
meal_revenue(hr, "meal", f_hotel = "Resort Hotel")
```

### .
```{r}
discount_ad(hr, "agent", f_hotel = "Resort Hotel")
```





# All {data-navmenu="Reservation" data-orientation="columns"}


## res_all_column1 {.tabset data-height=880 data-width=600}

### 2018
```{r}
guest_in_hotel(hr, 2018)
```

### 2019
```{r}
guest_in_hotel(hr, 2019)
```

### 2020
```{r}
guest_in_hotel(hr, 2020)
```


## res_all_column2 {data-height=440 data-width=400}

### {.no-title}
```{r}
changed_bookings(hr)
```

### {.no-title}
```{r}
channels(hr)
```



# City Hotel {data-navmenu="Reservation" data-orientation="rows"}


## res_ch_row1 {data-height=500 data-width=500}

###  {.no-title}
```{r}
reserved_assigned_room(hr, "City Hotel")
```

###  {.no-title}
```{r}
deposit_customer_type(hr, "City Hotel")
```


## res_ch_row2 {data-height=400 data-width=500}

### {.no-title}
```{r}
distribution_channel_lead_time(hr, "City Hotel")
```

### {.no-title}
```{r}
distribution_channel_res(hr, "City Hotel")
```


## res_ch_row3 {data-height=400 data-width=1000}

### {.no-title}
```{r}
agent_previous_cancellation(hr, "City Hotel", n = 20)
```


## res_ch_row4 {.tabset data-height=400 data-width=1000}

### Canceled
```{r}
reservation_status_date_count(hr, "Canceled", 2020, "City Hotel")
```

### Check-Out
```{r}
reservation_status_date_count(hr, "Check-Out", 2020, "City Hotel")
```

### No-Show
```{r}
reservation_status_date_count(hr, "No-Show", 2020, "City Hotel")
```



# Resort Hotel {data-navmenu="Reservation" data-orientation="rows"}


## res_ch_row1 {data-height=550 data-width=500}

###  {.no-title}
```{r}
reserved_assigned_room(hr, "Resort Hotel")
```

###  {.no-title}
```{r}
deposit_customer_type(hr, "Resort Hotel")
```


## res_ch_row2 {data-height=450 data-width=500}

### {.no-title}
```{r}
distribution_channel_lead_time(hr, "Resort Hotel")
```

### {.no-title}
```{r}
distribution_channel_res(hr, "Resort Hotel")
```


## res_ch_row3 {data-height=400 data-width=1000}

### {.no-title}
```{r}
agent_previous_cancellation(hr, "Resort Hotel", n = 20)
```


## res_ch_row4 {.tabset data-height=400 data-width=1000}

### Canceled
```{r}
reservation_status_date_count(hr, "Canceled", 2020, "Resort Hotel")
```

### Check-Out
```{r}
reservation_status_date_count(hr, "Check-Out", 2020, "Resort Hotel")
```

### No-Show
```{r}
reservation_status_date_count(hr, "No-Show", 2020, "Resort Hotel")
```





# All {data-navmenu="Guest" data-orientation="rows"}

## guest_all_row1 {data-height=400 data-width=1000 .tabset}

### 2018
```{r}
stays_arrival_date(hr, 2018)
```

### 2019
```{r}
stays_arrival_date(hr, 2019)
```

### 2020
```{r}
stays_arrival_date(hr, 2020)
```


## guest_all_row2 {data-height=600 data-width=1000 .tabset}

### 2018
```{r}
market_segment_guest(hr, 2018)
```

### 2019
```{r}
market_segment_guest(hr, 2019)
```

### 2020
```{r}
market_segment_guest(hr, 2020)
```



# City Hotel {data-navmenu="Guest" data-orientation="columns"}


## guest_ch_column1 {data-height=400 data-width=500}

### {.no-title}
```{r}
nationality_summary(hr, "count", "City Hotel")
```

### {.no-title}
```{r}
nationality_summary(hr, "lead_time", "City Hotel")
```

### {.no-title}
```{r}
market_segment_reserved_room_type(hr, "City Hotel")
```


## guest_ch_column2 {data-height=395 data-width=500}

### {.no-title}
```{r}
continent_summary(hr, "City Hotel")
```

### {.no-title}
```{r}
customer_type_reservation_status_count(hr, "City Hotel")
```

### {.no-title}
```{r}
meal_count(hr, "City Hotel")
```



# Resort Hotel {data-navmenu="Guest" data-orientation="columns"}


## guest_ch_column1 {data-height=400 data-width=500}

### {.no-title}
```{r}
nationality_summary(hr, "count", "Resort Hotel")
```

### {.no-title}
```{r}
nationality_summary(hr, "lead_time", "Resort Hotel")
```

### {.no-title}
```{r}
market_segment_reserved_room_type(hr, "Resort Hotel")
```


## guest_ch_column2 {data-height=395 data-width=500}

### {.no-title}
```{r}
continent_summary(hr, "Resort Hotel")
```

### {.no-title}
```{r}
customer_type_reservation_status_count(hr, "Resort Hotel")
```

### {.no-title}
```{r}
meal_count(hr, "Resort Hotel")
```

